О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
Shortify at one place
Thelinear estimate for the quantity of points on a line segment

	Consider $t$ such that $n^2 + 1 \leq t \leq (n+1)^2$. %,
	%then $f(t) > f(n^2 +1)$.% and $n \geq \sqrt{t} - 1$.
	For $t\in\mathbb{N}$ the inequality $(\sqrt{t} - 1)^2 +1 \leq t$ holds,
	thus
	%and derive that
	\begin{equation}
		\label{eq:line_segment_length}
		f(t) \geq f((\sqrt{t} - 1)^2 +1) \geq \frac{2}{3}(\sqrt{t} - 1)^3+\frac{1}{2}(\sqrt{t} - 1)^2-\frac{1}{6}(\sqrt{t} - 1)
		=
		\frac{2}{3}t^{3/2}-\frac{3}{2}t+\frac{5 }{6}t^{1/2}
		.
	\end{equation}
\end{proof}

@@

\begin{observation}
	\label{obs:estimate_points_on_straight_line}
	Let $\Delta$ be a straight line segment, $|\Delta| = l$ and $M \in \mathfrak{M}(2,n)$ for some $n>21491$.
	Let $\#(\Delta \cap M) = k > 10000$.
	Then $k \leq \gamma_2 b + 6$,
	where

	TODO!
\end{observation}

Now we are ready to proof the main theorem of the section.

>>>>

	%Consider $t$ such that $n^2 + 1 \leq t \leq (n+1)^2$. %,
	%then $f(t) > f(n^2 +1)$.% and $n \geq \sqrt{t} - 1$.
	For $t\in\mathbb{N}$ the inequality $(\sqrt{t} - 1)^2 +1 \leq t$ holds,
	thus
	%and derive that
	\begin{equation}
		\label{eq:line_segment_length}
		f(t) \geq f((\sqrt{t} - 1)^2 +1) \geq \frac{2}{3}(\sqrt{t} - 1)^3+\frac{1}{2}(\sqrt{t} - 1)^2-\frac{1}{6}(\sqrt{t} - 1)
		=
		\frac{2}{3}t^{3/2}-\frac{3}{2}t+\frac{5 }{6}t^{1/2}
		.
	\end{equation}
\end{proof}

@@

\begin{observation}
	\label{obs:estimate_points_on_straight_line}
	Let $\Delta$ be a straight line segment, $|\Delta| = b$ and $M \in \mathfrak{M}(2,n)$ for some $n$.
	Let $\#(\Delta \cap M) = k$ and $b>10000$.
	Then $k \leq \gamma_2 b + 6$,
	where
	\begin{equation}
		\gamma_2 = \frac{3846}{2593 \sqrt{647}-5823}
	\end{equation}
\end{observation}

\begin{proof}
	We are interested in integral $t$ such that estimate~\eqref{eq:estimate_for_segment_length}
	yields to $b > 10000$, because we know the maximum quantity of points for integral point sets of diameters at most $10000$.
	So, let us consider $t\geq 647$ and find a coefficient $\gamma_2$,
	such that the inequality
	\begin{equation}
		\label{eq:inequality_for_linear_estimate_of_segment_length}
		\frac{2}{3}t^{3/2}-\frac{3}{2}t+\frac{5 }{6}t^{1/2} \geq \frac{t-6}{\gamma_2}
	\end{equation}
	holds for all $t\geq 647$.
	For these $t$,
	the left part of~\eqref{eq:inequality_for_linear_estimate_of_segment_length} obviously grows faster than the right one.
	Turning~\eqref{eq:inequality_for_linear_estimate_of_segment_length} into the same equality
	and solving it for $t=647$, we obtain the claimed estimate.
\end{proof}

Now we are ready to prove the main theorem of the section.
